---
title: "W_UP_01"
author: "LuisJovelPalacios"
date: "fall 2025"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
boxplot(pushups~position,data=mydata)
```
  
The first qurtile of the "skill" players is bigger then the third quartile of the "line" players. I belive that what Dr. k told us that in theses situation there will be a statistical difference and that's what i think ill observe 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
  
I observed that there are a total of 8 "LINE" players and 22"SKIL" players. The avarge numbers of pushups that the "LINE" player can do is 17.12550, while the "SKILL" players on avarge can do 49.72727 pushups

## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```
The chances of getting a result like this if there is no difference in means between group "LINE" and group "SKILL" is equal to .000009421. Such a really low p-value like that allowed me to conclude that there is a really big margin between the "LINE" player and the "SKILL" player.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In this write up i learned how to plug in data whether its a boxplot or a favstats or t test. i was able to observe all the numerical data like for example in the boxplot chart. I was able to also analyze the "SKILL" players were able to do more pushups because their first quartile is already bigger than the "LINE" players third quartile. Another example is that in the favstats I was able to get the exact avarge number of pushups for the "LINE" as well as the "SKILL" player and their average number of pushups. Defently the "SKILL" playes had avrage number of pushups then the "LINE" players. I was able to get the p-value which waas .000009421 and this value is so low that made me sure my conclusion was really big margin between "LINE" and "SKILL" players.